Active Learning from Blackbox to Timed Connectors

### 2016-01-10 paper/paper.tex
new example

% used for flow charts
\usepackage{pgf}
\usepackage{tikz}
\usepackage{reotex}

@@

\title{Active Learning : From Blackbox To Timed Connectors}
\author{
\IEEEauthorblockN{Yi Li\IEEEauthorrefmark{1} and Meng Sun\IEEEauthorrefmark{1}}
\IEEEauthorblockA{
  \IEEEauthorrefmark{1}DI, School of Mathematical Sciences, Peking University,
  Beijing, China\\
  liyi\_math@pku.edu.cn, summeng@math.pku.edu.cn
}
}

\begin{document}
\maketitle
\begin{abstract}
  % reo coordination models
  Coordination languages provide a mean to formally specify the communication and
  reaction between different components. Such models play key roles in concurrent programming and
  large-scale distributed systems.
  % algorithms
  In this paper, an active learning framework is proposed to extract timed connectors from black-box
  systems.
  First of all, we introduce parameterized mealy machine as an operational semantics for
  channel-based coordination language Reo.
  Parameterized mealy machine serves as a bridge between Reo connectors and mealy machines. With
  production operator, complex connectors can be composed by basic channels and transformed into
  mealy machines. 
  Moreover, we adapt L*, a well-known learning algorithm, to timed connectors (in form of mealy
  machines). The new algorithm has shown its efficiency in multiple cases.
  % implementation
  Implementations of this framework is provided as a package in \texttt{Golang}.
\end{abstract}

@@

@@

If previous simulation results are stored in a well-maintained cache, the time-cost in
simulation process could be reduced signficiantly. In this work, we use a multiway tree to buffer
these results. A brief example of such trees can be found in Example \ref{example:tree}.

\begin{example}[Multiway-Tree Cache]
  \label{example:tree}
  Considering the FIFO channel presented in Example \ref{example:pmmfifo}. 
  \todo{draw a graph for multiway-tree cache}
\end{example}

\begin{table}[h]
  \renewcommand{\arraystretch}{1.3}
  \caption{Reduction of Membership Queries}
  \label{tabel:cacheoptimization}
  \centering
  \begin{tabular}{l||rrr}
    \hline
    & FIFO & Alternator & Gate \\
    \hline\hline
    Before & 93 & 880 & 1034 \\
    After & 90 & 725 & 707 \\
    Reduction Rate & 3.2\% & 21.4\% & 31.6\% \\
    \hline
  \end{tabular}
\end{table}

>>>>

% used for flow charts
\usepackage{pgf}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usepackage{reotex}

@@

\title{Active Learning from Blackbox to Timed Connectors}
\author{
\IEEEauthorblockN{Yi Li\IEEEauthorrefmark{1} and Meng Sun\IEEEauthorrefmark{1}}
\IEEEauthorblockA{
\IEEEauthorrefmark{1}Department of Informatics, School of Mathematical Sciences, Peking University,
Beijing, China\\
liyi\_math@pku.edu.cn, summeng@math.pku.edu.cn
}
}

  \begin{document}
\maketitle
\begin{abstract}
  Coordination models and languages play a key role in formally specifying the communication and
  interaction among different components in large-scale distributed and concurrent systems. In this
  paper, we propose an active learning framework to extract timed connector models from black-box
  system implementation. 
  We first introduce parameterized mealy machine as an operational semantic
  model for channel-based coordination language Reo. Parameterized mealy machine serves as a bridge
  between Reo connectors and mealy machines. With the product operator, complex connectors can be
  constructed by joining basic channels and transformed into mealy machines. Moreover, we adapt L*,
  a well-known learning algorithm, to timed connectors (in the form of mealy machines). The new
  algorithm has shown its efficiency in multiple case studies. 
  Implementations of this framework is provided as a package in \texttt{Golang}.
\end{abstract}

@@

\begin{figure}[h]
  \begin{center}
    \input{./images/reoextend.tex}
  \end{center}
  \caption{Merger and Replicator}
  \label{fig:reoextend}
\end{figure}

@@

If previous simulation results are stored in a well-maintained cache, the time-cost in
simulation process could be reduced signficiantly. In this work, we use a multiway tree to buffer
these results. A brief example of such trees can be found in Figure \ref{fig:multiway}.

\todo{the graph need further details}
\begin{example}[Multiway-Tree Cache]
  \label{example:tree}
  Considering the FIFO channel presented in Example \ref{example:pmmfifo}. 
  \begin{figure}[h]
    \begin{center}
      \input{./images/cache.tex}
    \end{center}
    \caption{Multiway-Tree Cache}
    \label{fig:multiway}
  \end{figure}
  Note that in this figure, only the edge information is stored. States like $q_0,q_a$ are written
  here only to make it clear.
\end{example}

\begin{table}[h]
  \renewcommand{\arraystretch}{1.3}
  \caption{Reduction of Membership Queries}
  \label{tabel:cacheoptimization}
  \centering
  \begin{tabular}{l||rrr}
    \hline
    & FIFO & Alternator & Gate \\
    \hline\hline
    Original Algorithm & 93 & 880 & 1034 \\
    Cached Algorithm & 90 & 725 & 707 \\
    Reduction Rate & 3.2\% & 21.4\% & 31.6\% \\
    \hline
  \end{tabular}
\end{table}

With cache applied, we have made a good reduction on the calls of membership queries. The results
can be found in Table \ref{tabel:cacheoptimization}.
